Reassessing the Impact of Dynamic Slicing in SFL

### 2019-01-20 paper/ijcai/paper.tex
new update
small fixes discussed in the last meeting

The contributions of this work are as follows:
\begin{itemize}
	\item A comprehensive study on the combination of \sfl{} and \ds{}
     for bug localization of \emph{Java} faulty programs.
	\item Empirical evidence that the \comb{} combination improves 
\end{itemize}

@@

\subsubsection{RQ1: \textit{How often DS misses faulty statements?}}

In \textbf{RQ1}, we evaluate how often DS misses faulty statements, since it is one of the main problems of dynamic slicing techniques.

@@

\begin{table}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	  \begin{tabular}{lccc}
		\toprule
		Project            & \# top-5 & \# top-10  & \% $\Delta$  \\ 
		\midrule
\lang{}            & 55 & 55 & 0 \%       \\   %\commentst{& 124   &  -}\\
		\cmath{}           & 87  & 91 & 3.77 \%     \\   %\comments{& 177   &  -}\\
		\closure{}         & 83  & 96  & 9.77 \%     \\   %\comments{& 350   &  -}\\
		\chart{}           & 22  & 24 & 7.69 \%      \\  %\comments{& 92    &  -}\\
		\jtime{}           & 21  & 27 & 3.70 \%       \\   %\comments{& 76    &  -}\\
		\mockito{}         & 24  & 27 & 7.89 \%    \\     %\comments{& 118   &  -}\\
		\bottomrule
	\end{tabular}
  \caption {Diagnosis capability if only considering the \sfl{} results for each version (no slicing applied)}
  \label{table:fsws}
\end{table}

@@

In \textbf{RQ2}, we pretend to evaluate the impact of combining \ds{} to improve \ds{}.

@@

\begin{table}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{cccc}
		\toprule
		Project             &  top-5  & top-10 & $\Delta$ \%\\ 
		\midrule
		\chart{}  & 59.30\% & 53.64\% & 5.66 \%\\ 		
		\bottomrule
	\end{tabular}
	\caption {\ds{} reduction performance for each version of the \chart{} project considering only the top-5 and top-10 classes}
	\label{tab:red}
\end{table}
\normalsize

>>>>

The contributions of this work are as follows:
\begin{itemize}
	\item A comprehensive study on the combination of \sfl{} and \ds{}
     for bug localization of \emph{Java} faulty programs.
	%\item Empirical evidence that the \comb{} combination improves 
\end{itemize}

@@

\subsubsection{RQ1: \textit{Diagnosis capability}}

\begin{table}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	  \begin{tabular}{lccc}
		\toprule
		Project            & \# top-5 & \# top-10  & \% $\Delta$  \\ 
		\midrule
		\lang{}            & 84.60 \% & 84.60 \% & 0 \%       \\   %\commentst{& 124   &  -}\\
		\cmath{}           & 82.08 \%  & 85.85 \% & 3.77 \%     \\   %\comments{& 177   &  -}\\
		\closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
		\chart{}           & 84.61 \%  & 92.31 \% & 7.70 \%      \\  %\comments{& 92    &  -}\\
		\jtime{}           & 77.78 \%  & 100.00 \% & 22.22 \%       \\   %\comments{& 76    &  -}\\
		\mockito{}         & 63.16 \%  & 71.05 \% & 7.89 \%    \\     %\comments{& 118   &  -}\\
		\bottomrule
	\end{tabular}
  \caption {Diagnosis capability if only considering the \sfl{} results for each version (no slicing applied)}
  \label{table:fsws}
\end{table}

\subsubsection{RQ2: \textit{How often DS misses faulty statements?}}

In \textbf{RQ2}, we evaluate how often DS misses faulty statements, since it is one of the main problems of dynamic slicing techniques.

@@

@@

In \textbf{RQ3}, we intend to evaluate the impact of combining \ds{} to improve \ds{}.

@@

\begin{table}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{ccc}
		\toprule
		Project             &  top-5  & top-10 \\ 
		\midrule
		\chart{}  & 59.30\% & 53.64\% \\ 		
		\bottomrule
	\end{tabular}
	\caption {\ds{} reduction performance for each version of the \chart{} project considering only the top-5 and top-10 classes}
	\label{tab:red}
\end{table}
\normalsize
